Windowed Residual-Minimization Model Reduction for Dynamical Systems

### 2019-09-19 main.tex
latest

\address[a]{Sandia National Laboratories,  Livermore, CA}
\begin{abstract}
This work proposes a \methodNameLower\ (\methodAcronym) model-reduction
	formulation for dynamical systems. The proposed approach minimizes the
	time-continuous full-order-model residual over a low-dimensional 
	trial subspace across a sequence of time windows and addresses key deficiencies in existing model-reduction approaches; e.g., the time-step and time-scheme dependence of least-squares Petrov--Galerkin (LSPG), the exponentially growing error bounds present in Galerkin and LSPG, and the offline cost of space--time LSPG. 
We consider two types of trial subspaces
	within the proposed framework:
	one that reduces the spatial dimension of the full-order model, and one that
	reduces both the spatial and temporal dimensions of the full-order model. For both types of trial spaces, we consider two differing solution techniques: direct (i.e., discretize-then-optimize) and indirect (i.e., optimize-then-discretize). Critically, we show that various instances of this framework yield existing model-reduction approaches, namely Galerkin, Least-Squares Petrov–Galerkin, and Space–Time Least-Squares Petrov– Galerkin. Numerical experiments on the compressible Euler and Navier--Stokes equations demonstrate that, at an increased computational cost, the \methodAcronym\ formulation can yield more accurate and physically relevant solutions than the Galerkin and Least-Squares Petrov--Galerkin approaches.

>>>>

\address[a]{Sandia National Laboratories,  Livermore, CA}
\begin{abstract}
This work proposes a \methodNameLower\ (\methodAcronym) model-reduction
	formulation for dynamical systems. The proposed approach minimizes the
	time-continuous full-order-model residual over a low-dimensional 
	trial subspace across a sequence of time windows and addresses key deficiencies in existing model-reduction approaches; e.g., the time step and time scheme dependence of least-squares Petrov--Galerkin (LSPG), the exponentially growing error bounds present in Galerkin and LSPG, and the offline cost of space--time LSPG. 
We consider two types of trial subspaces
	within the proposed framework:
	one that reduces the spatial dimension of the full-order model, and one that
	reduces both the spatial and temporal dimensions of the full-order model. For both types of trial spaces, we consider two differing solution techniques: direct (i.e., discretize-then-optimize) and indirect (i.e., optimize-then-discretize). Critically, we show that various instances of this framework yield existing model-reduction approaches, namely Galerkin, Least-Squares Petrov–Galerkin, and Space–Time Least-Squares Petrov– Galerkin. Numerical experiments on the compressible Euler and Navier--Stokes equations demonstrate that, at an increased computational cost, the \methodAcronym\ formulation can yield more accurate and physically relevant solutions than the Galerkin and Least-Squares Petrov--Galerkin approaches.
